Developing a Bubble Chamber Particle Discriminator Using Semi-Supervised Learning

### 2018-10-21 documentation/paper.tex
Mention specific events for audio and image samples

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{audio}
    \caption{\label{} An example of the cropped audio waveform $\omega$ and full resolution Fourier transform $\beta_{50,001}$ (recorded on 2016-12-02, run 1, event 21).}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.7\textwidth]{image_grid}
    \caption{\label{} An example of the image sequence $\iota$.}
\end{figure}

>>>>

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{audio}
    \caption{\label{} An example of the cropped audio waveform $\omega$ (on the left) and full resolution Fourier transform $\beta_{50,001}$ (on the right) for both audio channels. Recorded on 2016-12-02, run 1, event 21.}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.7\textwidth]{image_grid}
    \caption{\label{} An example of the image sequence $\iota$. Recorded on 2016-09-23, run 4, event 33.}
\end{figure}
